Clustering in a hyperbolic model of complex networks.

### 2019-02-21 concentration.tex
revised sections 6 and 7

Recall the adjusted triangle count function \eqref{eq:def_tilde_triangle_indicator}
\[
	\widetilde{T}_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in \BallPon{p}}\ind{p_2 \in \BallPon{p}}\ind{p_2 \in \BallPo{p_1} \cap \Rcal}.
\]
and the concentration set
\[
	\Kcal_C(k_n,n) = \left\{p \in \Rcal : \frac{k_n - C \kappa_n}{\xi} \vee 0 \le e^{\frac{y}{2}}
		\le \frac{k_n + C \kappa_n}{\xi} \right\},
\]
with
\[
	\kappa_n = \sqrt{k_n \log(k_n)}.
\]
We will define the corresponding triangle degree function
\begin{equation}\label{eq:def_degree_triangle_count_in_K}
	\widetilde{T}_{\Pcal,n}(k, C) = \sum_{p \in \Pcal_n \cap \Kcal_{C,n}(k_n)} \ind{\text{deg}_{\text{box}}(p) = k} \widetilde{T}_{\Pcal,n}(p),
\end{equation}
where 
\[
	\widetilde{T}_{\Pcal,n}(p) := \sum_{(p_1, p_2) \in \Pcal \setminus p}^{\ne} \widetilde{T}_{\Pcal,n}(p,p_1,p_2),
\]
where the sum is over all distinct pairs $(p_1, p_2) \in \Pcal \setminus p$.

>>>>

We define adjusted triangle count function as
\[
	\widetilde{T}_{\Pcal,n}(p_0,p_1,p_2) = \ind{p_1 \in \BallPon{p}}\ind{p_2 \in \BallPon{p}}\ind{p_2 \in \BallPo{p_1} \cap \Rcal}.
\]
and the concentration set
\[
	\Kcal_C(k_n,n) = \left\{p \in \Rcal : \frac{k_n - C \kappa_n}{\xi} \vee 0 \le e^{\frac{y}{2}}
		\le \frac{k_n + C \kappa_n}{\xi} \right\},
\]
with
\[
	\kappa_n = \sqrt{k_n \log(k_n)}.
\]
We will define the corresponding triangle degree function
\begin{equation}\label{eq:def_degree_triangle_count_in_K}
	\widetilde{T}_{\Pcal,n}(k, C) = \sum_{p \in \Pcal_n \cap \Kcal_{C,n}(k_n)} \ind{\text{deg}_{\text{box}}(p) = k} \widetilde{T}_{\Pcal,n}(p),
\end{equation}
where 
\[
	\widetilde{T}_{\Pcal,n}(p) := \sum_{(p_1, p_2) \in \Pcal \setminus p}^{\ne} \widetilde{T}_{\Pcal,n}(p,p_1,p_2),
\]
where the sum is over all distinct pairs $(p_1, p_2) \in \Pcal \setminus p$.

The following results follows from the proof of Proposition~\ref{prop:convergence_average_clustering_P_n}.

\begin{corollary}\label{cor:adjusted_triangle_counting_P_n}
Let $p_0 = (0,y)$. Then, uniformly for all $y \in \Kcal_C(k_n)$, as $n \to \infty$
\[
	\Exp{\widetilde{T}_{\text{box}}(p_0)} = (1+\smallO{1})\Exp{T_{\infty}(p_0)},
\]
where
\[
	\widetilde{T}_{\text{box}}(p_0) = \sum_{(p_1, p_2) \in \Pcal \setminus p_0}^{\ne} 
		\ind{p_1 \in \BallPon{p_0}}\ind{p_2 \in \BallPon{p_0}}\ind{p_2 \in \BallPo{p_1} \cap \Rcal}.
\]

In particular,
\[
	\binom{k_n}{2}^{-1}\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(p_0)} f(x,y) \dd x \dd y
	= (1+\smallO{1}) n \int_{\Rcal} \rho(y,k_n) P(y) \alpha e^{-\alpha y} \dd y. 
\]
\end{corollary}

\begin{proof}
First we note that equation~\eqref{eq:triangle_count_diff_scaling} implies that uniformly for $y \in \Kcal_C(k_n)$
\[
	\Exp{\left|\widetilde{T}_{\text{box}}(y) - T_{\infty}(y)\right|} = \bigO{n^{-(4\alpha - 2)}k_n^2}
	= \smallO{s(k_n) k_n^2},
\]
where the last part is due to Lemma~\ref{lem:scaling_s_alpha}.
Next, since $\Exp{T_\infty(y)} = \Mu{\BallPo{y}}^2 P(y)/2$, we get
\[
	\Exp{\widetilde{T}_{\text{box}}(y)} = \Exp{T_{\infty}(y)} + \Exp{\widetilde{T}_{\text{box}}(y) - T_{\infty}(y)} = \binom{k_n}{2} P(y) + \bigO{s(k_n)k_n^2},
\]
uniformly on $\Kcal_{C}(k_n)$. Therefore, we can apply a concentration of height argument to obtain
\begin{align*}
	&\hspace{-30pt}\binom{k_n}{2}^{-1}\int_{\Kcal_{C}(k_n)} \rho_{\text{box}}(y,k_n) \Exp{\widetilde{T}_{\text{box}}(y)} 
		f(x,y) \dd x \dd y\\
	&=\binom{k_n}{2}^{-1} n \int_{\Kcal_{C}(k_n)} \rho(y,k_n) \left(\binom{k_n}{2} P(y) + \bigO{s(k_n)k_n^2}\right)
		\alpha e^{-\alpha y} \dd y.....
\end{align*}
\PvdH{Finish this proof!}
\end{proof}
